\section*{Summary}
\addcontentsline{toc}{section}{Summary}

In recent mobile application development, the \textit{React Native} framework has gathered a large following because of it's cross-platform deployment approach. Developing and moving applications to production is made rather easy with the framework, both for the aforementioned cross-platform compatibility as well as the large availability of open source components that are free to use and offered on the internet.
\newline
However, a part often overlooked in \textit{React Native} development is testing. Many developers use manual testing on their applications by deploying them to testing devices or emulators while simply executing the actions a user would. This makes the development inefficient and the product unreliable due to the possibility of non-tested errors.
\newline
This research aims to answer the question how applications developed in \textit{React Native} can be tested properly, more specifically how end-to-end testing can be applied successfully in such a project. To do so, a collection of potential end-to-end testing frameworks is considered under defined circumstances, such as cross-platform compatibility, ease of use and necessary change to production code.
\newline
The testing framework are tested in the context of a project working on the application \textit{Connected.Football}. Conclusions are drawn both as to whether the testing frameworks are applicable to the project in question as well as how they can be used in a general \textit{React Native} project that is tested from the very beginning.